---
title: "Summary report for `r SelectStation`"
output: html_document
author: UKMON
date:   "`r Sys.Date()`"
---

```{r comment_block, echo = FALSE}
#=============================================================================
#
#-- Author: P Campbell-Burns, UKMON
#
#
#-- Description:
#
#   This script is an R Markdown / Knitr script that produces a summary report
#   for all meteor stereams and sporadics.  It uses generic report scripts
#   from the UKMON R Reporting suite.  Using Knitr the report is output as a 
#   Single HTML file with embedded images.
#
#-- Shared under the Creative Common  Non Commercial Sharealike 
#   License V4.0 (www.creativecommons.org/licebses/by-nc-sa/4.0/)
#
#-- Version history
#
#   Vers  Date          Notes
#   ----  ----          -----
#   1.0   07/12/2016    First release
#
#=============================================================================
```

```{r select_parameters, echo = FALSE}

max_loop = length(stations)/2
for (i in 1:max_loop) {
  if (stations[i*2-1] == as.character(SelectStation)) {
      cameras = stations[i*2]
  } 
}

```

```{r setup, echo=FALSE}

my <- ms[substr(ms$X_localtime,1,4)==CurrentYr,]
totalobs = nrow(my)
totalspo = nrow(my[my$X_stream=="SPO",])
totalstr = totalobs - totalspo

totalobs_all = nrow(ms)
totalspo_all = nrow(ms[ms$X_stream=="SPO",])
totalstr_all = totalobs_all - totalspo_all

Oper_since_yr = substr(min(ms$X_localtime),1,4)

has_stream <-    ( nrow(ms[ms$X_stream != "SPO",])) > 0
has_stream_yr <- ( nrow(my[my$X_stream != "SPO",])) > 0

fireball_count    <- nrow(ms[ms$X_mag <= -4,]) > 0
fireball_count_yr <- nrow(my[my$X_mag <= -4,]) > 0

```

# Summary of activity in `r CurrentYr`

`r SelectStation` operates `r length(cameras[[1]])` cameras.

In `r CurrentYr` `r SelectStation` has recorded `r totalobs` individual meteor observations.  These observations comprise `r totalspo` sporadic meteors and `r totalstr` stream meteors.  A breakdown by month is shown below.

```{r echo=FALSE, fig.height = 5, fig.extra='style="float:left"'}
MainTitle = paste(SelectStation, "observations by month")
outtab <- t(as.matrix(tabulate(as.numeric(substring(my$X_localtime,6,7)),nbins = 12)))
h = barplot(outtab,
         main=MainTitle,
         ylab = "Counts",
         border=FALSE,
         plot = TRUE,
         col="blue",
         cex.names = 0.6, 
         las=2,
         xaxt = "n")
axis(1, at = h, label = month.abb, padj = 0) 
box(which="plot",lty="solid")
```

`r if (has_stream_yr) {"The following shows observations by stream (preliminary UFO ANALYSIS classification):"}`

```{r echo=FALSE, fig.height = 5, fig.extra='style="float:left"', eval=has_stream_yr}
MainTitle = paste(SelectStation, "stream observations, station")
outtab <- sort(table(my[my$X_stream != "SPO","X_stream"]),decreasing=TRUE)
h = barplot(outtab[1:min(length(outtab))],
         main=MainTitle,
         ylab = "Counts",
         border=FALSE,
         plot = TRUE,
         col="blue",
         cex.names = 0.6, 
         las=2)
box(which="plot",lty="solid")
```

`r if (fireball_count_yr) {"## Fireball activity"}`

`r if (fireball_count_yr) {"(Based on IAU definition of apparrent magnitude of -4.0 of greater)"}`

```{r magtab1, echo=FALSE, eval=fireball_count_yr}
fireball <- my[my$X_mag <= -4, c("X_localtime","X_mag","X_stream", "X_dur",  "X_ID1")]
fireball <- fireball[, c("X_localtime","X_mag", "X_dur", "X_stream")]
fireball <- fireball[order(fireball$X_mag),]
colnames(fireball) <- c("Datetime","Magnitude", "Duration", "Stream")
kable(fireball,row.names=FALSE)
```

# All Observations

To date, station `r SelectStation` has recorded `r totalobs_all` individual meteor observations.  These observations comprise `r totalspo_all` sporadic meteors and `r totalstr_all` stream meteors.  A breakdown by year is given below.

```{r echo=FALSE, fig.height = 5, fig.extra='style="float:left"'}
MainTitle = paste(SelectStation, "Observations by year, station")
outtab <- t(as.matrix(table(substring(ms$X_localtime,1,4))))
h = barplot(outtab,
         main=MainTitle,
         ylab = "Counts",
         border=FALSE,
         plot = TRUE,
         col="blue",
         cex.names = 0.6, 
         las=2)
box(which="plot",lty="solid")
```

`r if (has_stream) {"The following graph shows observation counts by stream (preliminary UFO ANALYSIS classification).  A detailed breakdown by shower is given in the table at the end of this report."}`

```{r echo=FALSE, fig.height = 5, fig.extra='style="float:left"', eval = has_stream}
MainTitle = paste(SelectStation, "stream observations")
outtab <- sort(table(ms[ms$X_stream != "SPO","X_stream"]),decreasing=TRUE)
h = barplot(outtab[1:min(length(outtab),20)],
         main=MainTitle,
         ylab = "Counts",
         border=FALSE,
         plot = TRUE,
         col="blue",
         cex.names = 0.6, 
         las=2)
box(which="plot",lty="solid")
```

`r if (fireball_count) {"## Fireball activity"}`

`r if (fireball_count) {"(Based on IAU definition of apparrent magnitude of -4.0 of greater)"}`

```{r magtab2, echo=FALSE, eval=fireball_count}
fireball <- ms[ms$X_mag <= -4, c("X_localtime","X_mag", "X_dur", "X_stream", "X_ID1")]
fireball <- fireball[, c("X_localtime","X_mag", "X_dur", "X_stream")]
fireball <- fireball[order(fireball$X_mag),]
colnames(fireball) <- c("Datetime","Magnitude", "Duration", "Stream")
kable(fireball,row.names=FALSE)
```


`r if (has_stream) {"# Detailed counts (including sporadics)"}`

```{r, echo=FALSE, eval=has_stream}
outtab <- data.frame(sort(table(ms[,"X_stream"]),decreasing=TRUE))
colnames(outtab) <- c("Shower","Counts")
kable(outtab)
```


