---
output: html_document
---
```{r comment_block, echo = FALSE}
#=============================================================================
#
#-- Author: P Campbell-Burns, UKMON
#
#
#-- Description:
#
#   This script is an R Markdown / Knitr script that produces a summary report
#   for all meteor stereams and sporadics.  It uses generic report scripts
#   from the UKMON R Reporting suite.  Using Knitr the report is output as a
#   Single HTML file with embedded images.
#
#-- Shared under the Creative Common  Non Commercial Sharealike
#   License V4.0 (www.creativecommons.org/licebses/by-nc-sa/4.0/)
#
#-- Version history
#
#   Vers  Date          Notes
#   ----  ----          -----
#   1.1   14/03/2017    Report on SINGLE obs as well as UNIFIED data
#   1.0   07/12/2016    First release
#
#=============================================================================
```


```{r select_parameters, echo = FALSE}


#-- Filesystem parameters

root = "~/ANALYSIS"					 # Filesystem root (~ is users documents folder on Windows)

# Set report selection criteria

SelectYr      = 2017
SelectStream  = "ALL"
Streamname    = ""
Solpeak       = 46.28019
SelectStart   = "2017/01/02 00:00"
SelectEnd     = "2017/12/31 00:00"
```

```{r setup_libraries, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(xtable)
library(knitr)
library(tcltk)
```

```{r configure, echo = FALSE}
source(paste(root,"/CONFIG/Lib_Config.r",sep=""))
```
abort
```{r define_macros, echo=FALSE}

filter_apply_qa <- function(mx) {
  #===============================================================================
  #
  #-- Filters input data frame mx for all meteors meeting quality criteria
  #
  #===============================================================================
  #-- Filter input data frame by type (e.g. unified), stream, and year
  source(paste(root,"/CONFIG/Lib_QA.r",sep=""))
  n_start <- nrow(mx)
  cat("\n")
  cat(paste("QA filtering:\n"))
  cat(paste("=============\n"))    
  my<-subset(mx, X_dGP <= QA_dGP & X_QA >= QA_QA & abs(mx$X_dv12) <= QA_dv12 & abs(mx$X_Gm) >= QA_GM & X_dur >= QA_Dur & X_H1 <= QA_H1 & X_H2 >= QA_H2 & X_Qo >= QA_Qo & X_Qc >= QA_Qc )
  cat(paste("- dc12 <=",QA_dv12,"\n"))
  cat(paste("  dGP  <=",QA_dGP, "\n"))
  cat(paste("- GM   >=",QA_GM,  "\n"))  
  cat(paste("- Dur  >=",QA_Dur ,"\n"))
  cat(paste("- QA   >=",QA_QA,  "\n"))  
  cat(paste("- Qo   >=",QA_Qo,  "\n"))
  cat(paste("- Qc   >=",QA_Qc,  "\n"))  
  cat(paste("- H1   <=",QA_H1,  "\n"))  
  cat(paste("- H2   >=",QA_H2,  "\n\n"))
  n_end <- nrow(my)
  pct = 0
  if (n_end != 0) {pct = (100*n_end/n_start)}
  cat(paste("Rows out:",n_end,", ", round( 100 - pct ,digits=1),"% loss.\n"))    
  return (my)
  QA_Delta_GP
}

filter_stream <- function(mx, mstream="ALL", myr="ALL", mtype="UNIFIED") {
#===============================================================================
#-- Filters input data frame mx for all meteors meeting selection criteria
#-- (stream and year)
#===============================================================================
#-- Filter input data frame by type (e.g. unified), stream, and year
    if (mtype == "UNIFIED") {
	    my <- subset(mx, substring(X_ID1,2,8) == "UNIFIED")
	    my$X_ID1[nchar(my$X_ID1) == 11] <- sub("D_","D_0",my$X_ID1[nchar(my$X_ID1) == 11])
	   }
    if (mtype != "UNIFIED") my <- subset(mx, substring(X_ID1,2,8) != "UNIFIED")
    if (mstream != "ALL")  my <- subset(my, X_stream == mstream)
    if (myr     != "ALL")  my <- subset(my, substring(my$X_localtime,1,4) == myr)
    return (my)
}

```

```{r get_data, echo=FALSE}

OutType       = "CON"
runtime = format(Sys.time(),"%Y%m%d_%H%M")

SourceUnified    <-  "UKMON-all-unified.csv"   # Unified Obs File
SourceSingle     <-  "UKMON-all-single.csv"    # Single Obs File   

# - Read UFO Orbit data file

indir <- tk_choose.dir(caption = "Select source directory")
infile1 <- paste(indir,"/",SourceUnified,sep = "")
infile2 <- paste(indir,"/",SourceSingle,sep = "")

# --- Read the UFO data filea
mt <- read.csv(infile1, header=TRUE)
mm <- read.csv(infile2, header=TRUE)

# Standardise UNIFIED data
    mt$X_ID1<- substring(mt$X_ID1,2)
    mt$X_localtime <- as.POSIXct(strptime(mt$X_localtime, "_%Y%m%d_%H%M%S"))
    mt <- subset(mt, ! is.na(X_localtime))
    mt$X_stream <- toupper(ifelse(substring(mt$X_stream,1,2)=="_J",substring(mt$X_stream,5),substring(mt$X_stream,2)))

# Standardise SINGLETON data
    mm$X_ID1<- substring(mm$X_ID1,2)
    mm$X_localtime <- as.POSIXct(strptime(mm$X_localtime, "_%Y%m%d_%H%M%S"))
    mm <- subset(mm, ! is.na(X_localtime))
    mm$X_stream <- toupper(ifelse(substring(mm$X_stream,1,2)=="_J",substring(mm$X_stream,5),substring(mm$X_stream,2)))

if (is.factor(mt$X_amag)) {
  cat("Note: Problem detected in input data - amag converted from factor to numeric \n      Ignore next cooercion warnings")
  mt$X_amag <- as.numeric(as.character(mt$X_amag))
  mt <- mt[!is.na(mt$X_amag),]
  }

if (is.factor(mt$X_QA)) {
  cat("Note: Problem detected in input data - QA converted from factor to numeric")
  mt$X_QA <- as.numeric(as.character(mt$X_QA))
  mt <- mt[!is.na(mt$X_QA),]
  }

rows_read <- nrow(mt)
    if (rows_read == 0) {
        stop("No data in input file")
    }

mu <- filter_stream(mt, mstream=SelectStream, myr=SelectYr, mtype="UNIFIED")
ms <- filter_stream(mt, mstream=SelectStream, myr=SelectYr, mtype="OTHER")
mo <- filter_stream(mm, mstream=SelectStream, myr=SelectYr, mtype="OTHER")

if (nrow(mu) == 0) {
    stop(paste("No UNIFIED observations for stream",SelectStream,"were found in the input data"))
    } else {
            if (Apply_QA) {
                mu <- filter_apply_qa(mu)
            }
            rows_to_process <- nrow(mu)
            if (rows_to_process == 0) {
              stop ("No data to process - check / adjust QA filter settings")
            } else {

            # Set dataset title

                paste("Dataset:",SelectStream,"period",substring(min(mu$X_local),1,10),"to",substring(max(mu$X_local),1,10))



            # Run scripts relevant only to "ALL streams" plots


          }

    }
DataSet <- ""
select_dev <- function(Outfile=NA, Otype=NA, wd=NA, ht=NA, pp=NA)
 {

}

```
---
title: "Summary report `r SelectYr`"
output: html_document
author: UKMON
date: `r format(Sys.time(),"%B %d %Y")`
---

# Summary of activity

In `r SelectYr` a total of `r length(unique(mo$X_ID1))` cameras contributed data to the UKMON repository.  Together, these cameras recorded `r nrow(mo)` individual meteor observations.  The number of recorded observations by station is as follows:

```{r echo=FALSE, fig.height = 5, fig.extra='style="float:left"'}
par(mai=c(2.0,1.0,0.5,0.5))

outfile = paste(ReportDir,"/TABLE_Stream_Counts_by_Station_",SelectStream,"_",SelectYr,".csv",sep="")

MainTitle = paste("Total observations by station",Streamname)


# Restrict velocity to prevent range problems

outtab <- t(as.matrix(sort(table(mo$X_ID1),decreasing=TRUE)))

# Select and configure the output device

h = barplot(outtab,
         main=MainTitle,
         ylab = "Counts",
         border=FALSE,
         plot = TRUE,
         col="blue",
         cex.names = 0.6,
         las=2)

title(sub=DataSet,line=6)

rm(outtab)
rm(h)
box(which="plot",lty="solid")
```

After applying quality criteria we found that `r rows_to_process` meteors were observed by more than one camera (Unified observations).  The following shows a count of the number of meters observed by two, three, etc. cameras.

```{r echo=FALSE, fig.height = 5, fig.extra='style="float:left"'}
source(paste(PlotDir,"stream_plot_by_correllation.r",sep="/"),local=TRUE)
box(which="plot",lty="solid")
```

The number of unified observations as a percentage of individual observations is `r sprintf("%.1f",100*rows_to_process/nrow(mo))`%.  A breakdown of unified observation counts by stream (top ten) is as follows:

```{r echo=FALSE, fig.height = 5, fig.extra='style="float:left"'}
source(paste(PlotDir,"streamcounts.r",sep="/"),local=TRUE)
box(which="plot",lty="solid")
```



## Fireball activity

A total of `r nrow(mu[mu$X_mag <= -4,])` fireballs were observed in the reporting period (`r SelectYr`).  A breakdown by months and by shower is shown below.

```{r echo=FALSE, fig.height = 5, fig.extra='style="float:left"'}
source(paste(PlotDir,"fireball_by_month.r",sep="/"),local=TRUE)
box(which="plot",lty="solid")
```

```{r echo=FALSE, fig.height = 5, fig.extra='style="float:left"'}
source(paste(PlotDir,"fireball_by_stream.r",sep="/"),local=TRUE)
box(which="plot",lty="solid")
```

The top 10 brightest fireballs were:

```{r magtab, echo=FALSE}
fireball <- mu[mu$X_mag <= -4, c("X_localtime","X_mag","X_stream","X_ID1")]
fireball$X_matches <- ifelse(substr(fireball$X_ID1,10,10)=="0",substr(fireball$X_ID1,11,11),substr(fireball$X_ID1,10,11))
fireball <- fireball[, c("X_localtime","X_mag","X_stream","X_matches")]
fireball <- fireball[order(fireball$X_mag),]
maxrow = min(nrow(fireball),10)
colnames(fireball) <- c("Datetime","Magnitude", "Stream","Station matches")
kable(fireball[1:maxrow,],row.names=FALSE)
```



## Velocity distribution

The following graphs show the distribution of velocities:


```{r echo=FALSE, fig.height = 5, fig.extra='style="float:left"'}
source(paste(PlotDir,"stream_plot_vel.r",sep="/"),local=TRUE)
box(which="plot",lty="solid")
```

## Magnitudes

The following graphs show the distribution of magnitudes:

```{r echo=FALSE, fig.height = 5, fig.extra='style="float:left"'}
source(paste(PlotDir,"stream_plot_mag.r",sep="/"),local=TRUE)
box(which="plot",lty="solid")
```

```{r echo=FALSE, fig.height = 5, fig.extra='style="float:left"'}
source(paste(PlotDir,"abs_magnitude_vs_h1_h2_reg.r",sep="/"),local=TRUE)
box(which="plot",lty="solid")
```

The following plots shows the altitude of the atart and end of ablation for each individual meteor.  The plot is in order of decreasing start height and gives a good visualisation of the depth of the ablation zone.  Where in the atmosphere ablation occurs will depend on factors such as meteor velocity and composition.

```{r echo=FALSE, fig.height = 5, fig.extra='style="float:left"'}
source(paste(PlotDir,"stream_ablation.r",sep="/"),local=TRUE)
```

The maximum observed altitude was `r sprintf("%.1f",max(mu$X_H1))` km and the minimum observed altitude was `r sprintf("%.1f",min(mu$X_H2))` km.  The distribution of distances travelled through the ablation zone was as follows:

```{r echo=FALSE, fig.height = 5, fig.extra='style="float:left"'}
source(paste(PlotDir,"observed_trajectory_LD21.r",sep="/"),local=TRUE)
box(which="plot",lty="solid")
```

## Other Data of Interest

```{r echo=FALSE, fig.height = 5, fig.extra='style="float:left"' }
source(paste(PlotDir,"semimajor_v_ascending.r",sep="/"),local=TRUE)
box(which="plot",lty="solid")
```

## Data matching

The following table shows the camera pairings that are producing the highest number of unified observations.

```{r echo=FALSE, eval = (nrow(mt) > 0),fig.height = 5, fig.extra='style="float:left"'}

tmp <- subset(mt,substring(mt$X_ID1,2,8) != "UNIFIED")
tmp$X_ID2 = substr(tmp$X_ID2,2,30)
outtab <- table(tmp$X_ID1,tmp$X_ID2)
unified <- data.frame()
for (irow in 1: nrow(outtab)) {

  for (icol in 1:min(irow,ncol(outtab))) {
    if (outtab[irow,icol] != 0) {
      unified <- rbind( unified, data.frame(row.names(outtab)[irow], colnames(outtab)[icol], outtab[irow,icol] ))
    }

  }
}
colnames(unified) <- c("Station_1", "Station_2", "Paired_Observations")
unified <- unified[order(unified$Paired_Observations, decreasing = TRUE),]
kable(unified[1:20,],row.names=FALSE)
```

```{r echo=FALSE, fig.height = 5, fig.extra='style="float:left"' }
source(paste(PlotDir,"semiMajor_v_inclination.r",sep="/"),local=TRUE)
box(which="plot",lty="solid")
```

## Data Quality Indicators

The following plot shows the average linearity error in the processing of data:

```{r echo=FALSE, fig.height = 5, fig.extra='style="float:left"' }
source(paste(PlotDir,"cdeg_overall.r",sep="/"),local=TRUE)
box(which="plot",lty="solid")
```

The following graph shows the distribution of differences in velocity between matched observations:

```{r echo=FALSE, fig.height = 5, fig.extra='style="float:left"' }
source(paste(PlotDir,"delta_vo_overall.r",sep="/"),local=TRUE)
box(which="plot",lty="solid")
```
