---
output: html_document
---
```{r comment_block, echo = FALSE}
#=============================================================================
#
#-- Author: P Campbell-Burns, UKMON
#
#
#-- Description:
#
#   This script is an R Markdown / Knitr script that produces a summary report
#   for all a selected meteor steream.  It uses generic report scripts
#   from the UKMON R Reporting suite.  Using Knitr the report is output as a 
#   Single HTML file with embedded images.
#
#-- Shared under the Creative Common  Non Commercial Sharealike 
#   License V4.0 (www.creativecommons.org/licebses/by-nc-sa/4.0/)
#
#-- Version history
#
#   Vers  Date          Notes
#   ----  ----          -----
#   1.2   14/03/2017    Improved narrative and bug fixes
#   1.1   09/02/2017    Moved root path from config file to improve MacOS compatibility
#   1.0   07/12/201y    First release
#
#=============================================================================
```

```{r run_parameters, echo = FALSE}

#-- Filesystem parameters

root = "~/ANALYSIS"					 # Filesystem root (~ is users documents folder on Windows)

# Set report selection criteria

SelectYr      = 2017
SelectStream  = "PER"
Streamname    = "Perseids"
Solpeak       = 139.212097	
SelectStart   = paste(SelectYr,"/01/01 00:00",sep="")
SelectEnd     = paste(SelectYr,"/12/31 00:00",sep="")
Apply_QA      = FALSE
```


```{r setup_libraries, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(xtable)
library(knitr)
```

```{r setup_environment, echo = FALSE}

source(paste(root,"/CONFIG/Lib_Config.r",sep=""))
```

```{r define_macros, echo=FALSE}

filter_apply_qa <- function(mx) {
  #===============================================================================
  #
  #-- Filters input data frame mx for all meteors meeting quality criteria
  #
  #===============================================================================
  #-- Filter input data frame by type (e.g. unified), stream, and year
  source(paste(root,"/CONFIG/Lib_QA.r",sep="")) 
  n_start <- nrow(mx)
  cat("\n")
  cat(paste("QA filtering:\n")) 
  cat(paste("=============\n"))    
  my<-subset(mx, X_dGP <= QA_dGP & X_QA >= QA_QA & abs(mx$X_dv12) <= QA_dv12 & abs(mx$X_Gm) >= QA_GM & X_dur >= QA_Dur & X_H1 <= QA_H1 & X_H2 >= QA_H2 & X_Qo >= QA_Qo & X_Qc >= QA_Qc )
  cat(paste("- dc12 <=",QA_dv12,"\n")) 
  cat(paste("  dGP  <=",QA_dGP, "\n"))
  cat(paste("- GM   >=",QA_GM,  "\n"))  
  cat(paste("- Dur  >=",QA_Dur ,"\n")) 
  cat(paste("- QA   >=",QA_QA,  "\n"))  
  cat(paste("- Qo   >=",QA_Qo,  "\n")) 
  cat(paste("- Qc   >=",QA_Qc,  "\n"))  
  cat(paste("- H1   <=",QA_H1,  "\n"))  
  cat(paste("- H2   >=",QA_H2,  "\n\n")) 
  n_end <- nrow(my)
  pct = 0
  if (n_end != 0) {pct = (100*n_end/n_start)}
  cat(paste("Rows out:",n_end,", ", round( 100 - pct ,digits=1),"% loss.\n"))    
  return (my)
  QA_Delta_GP
}


filter_stream <- function(mx, mstream="ALL", myr="ALL", mtype="UNIFIED") {
#===============================================================================
#-- Filters input data frame mx for all meteors meeting selection criteria
#-- (stream and year)
#===============================================================================
#-- Filter input data frame by type (e.g. unified), stream, and year
    if (mtype == "UNIFIED") {
	    my <- subset(mx, substring(X_ID1,2,8) == "UNIFIED")
	    my$X_ID1[nchar(my$X_ID1) == 11] <- sub("D_","D_0",my$X_ID1[nchar(my$X_ID1) == 11])
	   }
    if (mtype != "UNIFIED") my <- subset(mx, substring(X_ID1,2,8) != "UNIFIED")
    if (mstream != "ALL")  my <- subset(my, X_stream == mstream)
    if (myr     != "ALL")  my <- subset(my, substring(my$X_localtime,1,4) == myr)
    return (my)
}

read_ufo <- function(mx) {
#===============================================================================
#
#-- Presents file picker filtered for CSV files (if no preconfigured input file)
#-- Ingests file
#-- Standardises data
#
#===============================================================================

library(tcltk)
    
# setup filter
    filt <- matrix(c("Comma separated / Excel files","*.csv"), 
            nrow = 1, ncol = 2, byrow = TRUE,
            dimnames = list(c("csv"),c("V1","V2")))
    
if (is.na(SourceUnified)) {
        infile <- tk_choose.files(caption = "Select UFO Orbit Unified file",multi = FALSE,filters=filt)
	} else {
        infile <- paste(DataDir,SourceUnified,sep="/")
	}

if (infile == "") stop

# --- Read the UFO data file

# Read raw data
    mt <- read.csv(infile, header=TRUE)

# Standardise ID1
    mt$X_ID1<- substring(mt$X_ID1,2)

# standardise localtime
    mt$X_localtime <- as.POSIXct(strptime(mt$X_localtime, "_%Y%m%d_%H%M%S"))

# remove NA localtimes if any
    mt <- subset(mt, ! is.na(X_localtime))

# Standardise streamname
    mt$X_stream <- toupper(ifelse(substring(mt$X_stream,1,2)=="_J",substring(mt$X_stream,5),substring(mt$X_stream,2)))

return (mt)

}

```

```{r import_data, echo=FALSE}

OutType       = "CON"
runtime = format(Sys.time(),"%Y%m%d_%H%M")
  
mt <- read_ufo()
    
if (is.factor(mt$X_amag)) {
  cat("Note: Problem detected in input data - amag converted from factor to numeric \n      Ignore next cooercion warnings")
  mt$X_amag <- as.numeric(as.character(mt$X_amag))
  mt <- mt[!is.na(mt$X_amag),]
  }
    
if (is.factor(mt$X_QA)) {
  cat("Note: Problem detected in input data - QA converted from factor to numeric")
  mt$X_QA <- as.numeric(as.character(mt$X_QA))
  mt <- mt[!is.na(mt$X_QA),]
  }
    
rows_read <- nrow(mt)
    if (rows_read == 0) {
        stop("No data in input file")
    } 

mu <- filter_stream(mt, mstream=SelectStream, myr=SelectYr, mtype="UNIFIED")
ms <- filter_stream(mt, mstream=SelectStream, myr=SelectYr, mtype="OTHER")
    
if (nrow(mu) == 0) {
    stop(paste("No UNIFIED observations for stream",SelectStream,"were found in the input data"))
    } else {
            if (Apply_QA) {
                mu <- filter_apply_qa(mu)
            }
            rows_to_process <- nrow(mu)
            if (rows_to_process == 0) {
              stop ("No data to process - check / adjust QA filter settings")
            } else {
            
            # Set dataset title
            
                paste("Dataset:",SelectStream,"period",substring(min(mu$X_local),1,10),"to",substring(max(mu$X_local),1,10))
            


            # Run scripts relevant only to "ALL streams" plots
            

          }
    
    }
DataSet <- ""
select_dev <- function(Outfile=NA, Otype=NA, wd=NA, ht=NA, pp=NA)
  
 {
  
}

```
---
title: "`r SelectYr` `r Streamname`"
output: html_document
author: UKMON
date: 27 Nov 2016
---

# Summary of activity

After processing of data by UFO_ORBIT and applying appropriate quality criteria, a total of `r nrow(ms)` `r Streamname` observations were recorded by indvidual stations which which could be matched with more than one station. the following graph shows matched observation counts by station:

```{r echo=FALSE, fig.height = 5, fig.extra='style="float:left"'}
source(paste(PlotDir,"streamcounts_plot_by_station.r",sep="/"),local=TRUE)
box(which="plot",lty="solid")
```

The number of unified observations meeting quality criteria as a percentage of individual observations was `r rows_to_process` from `r nrow(ms)` individual station observations (`r sprintf("%.1f",100*rows_to_process/nrow(ms))`)%.  

```{r echo=FALSE, fig.height = 5, fig.extra='style="float:left"'}
source(paste(PlotDir,"stream_plot_by_correllation.r",sep="/"),local=TRUE)
box(which="plot",lty="solid")
```

The number of (matched) individual station observations over time is as follows:

```{r echo=FALSE, fig.height = 5, fig.extra='style="float:left"'}
source(paste(PlotDir,"stream_plot_timeline_single.r",sep="/"),local=TRUE)
box(which="plot",lty="solid")
```

## Velocity distribution of `r Streamname`

The graph below shows the distribution of velocities for the `r Streamname`. 

```{r echo=FALSE, fig.height = 5, fig.extra='style="float:left"'}
source(paste(PlotDir,"stream_plot_vel.r",sep="/"),local=TRUE)
box(which="plot",lty="solid")
```

## Magnitudes 

The graph below shows the distribution of magnitudes for the `r Streamname`:

```{r echo=FALSE, fig.height = 5, fig.extra='style="float:left"'}
source(paste(PlotDir,"stream_plot_mag.r",sep="/"),local=TRUE)
box(which="plot",lty="solid")
```

The following graph shows the relationship between start and end heights of the observed `r Streamname` meteors and their absolute magnitudes:

```{r echo=FALSE, fig.height = 5, fig.extra='style="float:left"'}
source(paste(PlotDir,"abs_magnitude_vs_h1_h2_reg.r",sep="/"),local=TRUE)
box(which="plot",lty="solid")
```

The altitudes at which ablation was visible is shown in the plot below

```{r echo=FALSE, fig.height = 5, fig.extra='style="float:left"'}
source(paste(PlotDir,"stream_ablation.r",sep="/"),local=TRUE)
```

The maximum start heigh was `r sprintf("%.1f",max(mu$X_H1))` km and the minimum end height was `r sprintf("%.1f",min(mu$X_H2))` km.  The distribution of distances travelled through the ablation zone was as follows:

```{r echo=FALSE, fig.height = 5, fig.extra='style="float:left"'}
source(paste(PlotDir,"observed_trajectory_LD21.r",sep="/"),local=TRUE)
box(which="plot",lty="solid")
```

## Shower Radiant

```{r echo=FALSE, fig.height = 5, fig.extra='style="float:left"'}
source(paste(PlotDir,"stream_plot_radiant.r",sep="/"),local=TRUE)
```

Movement of the radiant over the duration of the `r Streamname' is shown in the following plot.

```{r echo=FALSE, fig.height = 5, fig.extra='style="float:left"'}
source(paste(PlotDir,"stream_plot_radiant_movement.r",sep="/"),local=TRUE)
```

## Other Data of Interest

```{r echo=FALSE, fig.height = 5, fig.extra='style="float:left"' }
source(paste(PlotDir,"semimajor_v_ascending.r",sep="/"),local=TRUE)
box(which="plot",lty="solid")
```

```{r echo=FALSE, fig.height = 5, fig.extra='style="float:left"' }
source(paste(PlotDir,"semiMajor_v_inclination.r",sep="/"),local=TRUE)
box(which="plot",lty="solid")
```

## Data Quality indicators

The following plot shows the average linearity error in the processed data:

```{r echo=FALSE, fig.height = 5, fig.extra='style="float:left"' }
source(paste(PlotDir,"cdeg_overall.r",sep="/"),local=TRUE)
box(which="plot",lty="solid")
```

The following graph shows the distribution of differences in velocity between matched observations:

```{r echo=FALSE, fig.height = 5, fig.extra='style="float:left"' }
source(paste(PlotDir,"delta_vo_overall.r",sep="/"),local=TRUE)
box(which="plot",lty="solid")
```


```{r setup, echo=FALSE}
fireball_count    <- nrow(mu[mu$X_mag <= -4,]) > 0
```

`r if (fireball_count) {"## Bright stream meteors"}`

`r if (fireball_count) {"The following table shows meteors which meet the IAU definition of a fireball (apparrent magnitude of -4.0 of brighter).  Only unified observations are shown"}`


```{r magtab2, echo=FALSE, eval=fireball_count}
fireball <- mu[mu$X_mag <= -4, c("X_localtime","X_mag", "X_dur", "X_ID1")]
fireball <- fireball[, c("X_localtime","X_mag", "X_dur")]
fireball <- fireball[order(fireball$X_mag),]
colnames(fireball) <- c("Datetime","Magnitude", "Duration")
kable(fireball,row.names=FALSE)
